%Bibliografía
%
\begin{thebibliography}{9}
\addcontentsline{toc}{chapter}{Bibliografía}
\chaptermark{Bibliograf\'{\i}a}

\bibitem{dickson} L.E. Dickson (1914) \textit{Algebraic Invariants}. Mathematical Monographs No. 14. New York: John Wiley \& Sons.

\bibitem{hermite} C. Hermite (1858) Sur la résolution de l'équation du cinqui\`eme degré. \textit{C.R.Math. Acad. Sci. Paris}. {\bf 46}, 508-515.

\bibitem{hilbert} D. Hilbert (1897) \textit{Theory of Algebraic Invariants}. Lectures prepared by Sophus Marxsen. Translated into English by Reinhard C. Laubenbacher (1993). Cambridge, UK: The Press Syndicate of the University of Cambridge.

\bibitem{hippenmeyer} C. Hippenmeyer (1979) Die Anzahl der inkongruenten ebenen Netze eines regulären Ikosaeders. \textit{Elemente der Mathematik}. {\bf 34}, 61-63.

\bibitem{klein} F. Klein (1884) \textit{Vorlesungen über das Ikosaeder und die Auflösung der Gleichungen vom fünften Grade.} Leipzig: Teubner. English translation by G. G. Morrice (1956) \textit{Lectures on the Icosahedron and the solution of equations of fifth degree.} New York: Dover Publications. 

\bibitem{mckeanmoll} H. McKean and V. Moll (1997) \textit{Elliptic curves.} Cambridge: Cambridge University Press.

\bibitem{nash} O. Nash (2013) \textit{On Klein's Icosahedral Solution of the Quintic}. {\tt http:// arxiv.org/pdf/1308.0955.pdf}, 10.28.2015.

\bibitem{olsen} J. Olsen (2010) \textit{The Geometry of Möbius Transformations}. University of Rochester.

\bibitem{reid} M. Reid (1988) \textit{Undergraduate Algebraic Geometry}. Cambridge: Cambridge University Press.

\bibitem{shurman} J. Shurman (1997) \textit{Geometry of the Quintic}. New York: John Wiley \& Sons.

\end{thebibliography}